02_DESeq_hyp

### 2019-04-05 analysis/02_DESeq2_hyp.Rmd
now with for loop to count degs

colData$group <- paste(colData$sex, colData$tempgroup, sep = "")
colData$group <- as.factor(colData$group)
str(colData$group)
```

@@

```{r res}
levels(colData$treatment) 
summary(results(dds, contrast=c("treatment",'control', 'bldg')))    #3502 2450
summary(results(dds, contrast=c("treatment",'control', 'lay')))     #3581 2642
summary(results(dds, contrast=c("treatment",'control', 'inc.d3')))  #3956 2802
summary(results(dds, contrast=c("treatment",'control', 'inc.d9')))  #3968 2985
summary(results(dds, contrast=c("treatment",'control', 'inc.d17'))) #3949 2724
summary(results(dds, contrast=c("treatment",'control', 'hatch')))   #3600 2660
summary(results(dds, contrast=c("treatment",'control', 'n5')))      #4080 2842
summary(results(dds, contrast=c("treatment",'control', 'n9')))      #4035 2979

summary(results(dds, contrast=c("treatment",'bldg', 'lay')))     #1   0
summary(results(dds, contrast=c("treatment",'bldg', 'inc.d3')))  #0   0 
summary(results(dds, contrast=c("treatment",'bldg', 'inc.d9')))  #5   0 
summary(results(dds, contrast=c("treatment",'bldg', 'inc.d17'))) #0   0 
summary(results(dds, contrast=c("treatment",'bldg', 'hatch')))   #1   2
summary(results(dds, contrast=c("treatment",'bldg', 'n5')))      #10  3
summary(results(dds, contrast=c("treatment",'bldg', 'n9')))      #168 124

summary(results(dds, contrast=c("treatment",'lay', 'bldg')))    #    1
summary(results(dds, contrast=c("treatment",'lay', 'inc.d3')))  #0   0   
summary(results(dds, contrast=c("treatment",'lay', 'inc.d9')))  #5   6 
summary(results(dds, contrast=c("treatment",'lay', 'inc.d17'))) #2   2 
summary(results(dds, contrast=c("treatment",'lay', 'hatch')))   #3   8 
summary(results(dds, contrast=c("treatment",'lay', 'n5')))      #1   0
summary(results(dds, contrast=c("treatment",'lay', 'n9')))      #135 194

summary(results(dds, contrast=c("treatment",'inc.d3', 'bldg')))    #0 0 
summary(results(dds, contrast=c("treatment",'inc.d3', 'lay')))     #0 0 
summary(results(dds, contrast=c("treatment",'inc.d3', 'inc.d9')))  #1 0
summary(results(dds, contrast=c("treatment",'inc.d3', 'inc.d17'))) #0 0   
summary(results(dds, contrast=c("treatment",'inc.d3', 'lay')))     #0 0 
summary(results(dds, contrast=c("treatment",'inc.d3', 'n5')))      #0 0 
summary(results(dds, contrast=c("treatment",'inc.d3', 'n9')))      #0 0

summary(results(dds, contrast=c("treatment",'inc.d9', 'inc.d17'))) #2 3  
summary(results(dds, contrast=c("treatment",'inc.d9', 'lay')))     #6 5
summary(results(dds, contrast=c("treatment",'inc.d9', 'n5')))      #0 1
summary(results(dds, contrast=c("treatment",'inc.d9', 'n9')))      #0 2

summary(results(dds, contrast=c("treatment",'inc.d17', 'lay'))) #2   2
summary(results(dds, contrast=c("treatment",'inc.d17', 'n5')))  #2   4
summary(results(dds, contrast=c("treatment",'inc.d17', 'n9')))  #131 136

summary(results(dds, contrast=c("treatment",'hatch', 'bldg')))    #2   1    
summary(results(dds, contrast=c("treatment",'hatch', 'lay')))     #8   3  
summary(results(dds, contrast=c("treatment",'hatch', 'inc.d3')))  #524 406 
summary(results(dds, contrast=c("treatment",'hatch', 'inc.d9')))  #1106 1169 
summary(results(dds, contrast=c("treatment",'hatch', 'inc.d17'))) #3    0 
summary(results(dds, contrast=c("treatment",'hatch', 'n5')))      #1076 875
summary(results(dds, contrast=c("treatment",'hatch', 'n9')))      #898  845

summary(results(dds, contrast=c("treatment",'n5', 'bldg')))    #3   10 
summary(results(dds, contrast=c("treatment",'n5', 'lay')))     #0   1 
summary(results(dds, contrast=c("treatment",'n5', 'inc.d3')))  #0   0 
summary(results(dds, contrast=c("treatment",'n5', 'inc.d9')))  #1   0 
summary(results(dds, contrast=c("treatment",'n5', 'inc.d17'))) #4   2 
summary(results(dds, contrast=c("treatment",'n5', 'hatch')))   #875 1076 
summary(results(dds, contrast=c("treatment",'n5', 'n9')))      #0   0

summary(results(dds, contrast=c("treatment",'n9', 'bldg')))    #124 168 
summary(results(dds, contrast=c("treatment",'n9', 'lay')))     #194 135 
summary(results(dds, contrast=c("treatment",'n9', 'inc.d3')))  #0   0 
summary(results(dds, contrast=c("treatment",'n9', 'inc.d9')))  #2   0 
summary(results(dds, contrast=c("treatment",'n9', 'inc.d17'))) #136 131 
summary(results(dds, contrast=c("treatment",'n9', 'hatch')))   #845 898 
summary(results(dds, contrast=c("treatment",'n9', 'n5')))      #0   0 
```

```{r totalDEGs}
levels(colData$treatment)

totalDEGs(c("treatment", 'bldg','lay'))
totalDEGs(c("treatment", 'bldg','inc.d3'))
totalDEGs(c("treatment", 'bldg','inc.d9'))
totalDEGs(c("treatment", 'bldg','inc.d17'))
totalDEGs(c("treatment", 'bldg','hatch'))
totalDEGs(c("treatment", 'bldg','n5'))
totalDEGs(c("treatment", 'bldg','n9'))

totalDEGs(c("treatment", 'lay','bldg'))
totalDEGs(c("treatment", 'lay','inc.d3'))
totalDEGs(c("treatment", 'lay','inc.d9'))
totalDEGs(c("treatment", 'lay','inc.d17'))
totalDEGs(c("treatment", 'lay','hatch'))
totalDEGs(c("treatment", 'lay','n5'))
totalDEGs(c("treatment", 'lay','n9'))

totalDEGs(c("treatment", 'inc.d3','bldg'))
totalDEGs(c("treatment", 'inc.d3','lay'))
totalDEGs(c("treatment", 'inc.d3','inc.d9'))
totalDEGs(c("treatment", 'inc.d3','inc.d17'))
totalDEGs(c("treatment", 'inc.d3','hatch'))
totalDEGs(c("treatment", 'inc.d3','n5'))
totalDEGs(c("treatment", 'inc.d3','n9'))

totalDEGs(c("treatment", 'inc.d9','bldg'))
totalDEGs(c("treatment", 'inc.d9','lay'))
totalDEGs(c("treatment", 'inc.d9','inc.d3'))
totalDEGs(c("treatment", 'inc.d9','inc.d17'))
totalDEGs(c("treatment", 'inc.d9','hatch'))
totalDEGs(c("treatment", 'inc.d9','n5'))
totalDEGs(c("treatment", 'inc.d9','n9'))

totalDEGs(c("treatment", 'inc.d17','bldg'))
totalDEGs(c("treatment", 'inc.d17','lay'))
totalDEGs(c("treatment", 'inc.d17','inc.d3'))
totalDEGs(c("treatment", 'inc.d17','inc.d9'))
totalDEGs(c("treatment", 'inc.d17','hatch'))
totalDEGs(c("treatment", 'inc.d17','n5'))
totalDEGs(c("treatment", 'inc.d17','n9'))

totalDEGs(c("treatment", 'hatch','bldg'))
totalDEGs(c("treatment", 'hatch','lay'))
totalDEGs(c("treatment", 'hatch','inc.d3'))
totalDEGs(c("treatment", 'hatch','inc.d9'))
totalDEGs(c("treatment", 'hatch','inc.d17'))
totalDEGs(c("treatment", 'hatch','n5'))
totalDEGs(c("treatment", 'hatch','n9'))

totalDEGs(c("treatment", 'n5','bldg'))
totalDEGs(c("treatment", 'n5','lay'))
totalDEGs(c("treatment", 'n5','inc.d3'))
totalDEGs(c("treatment", 'n5','inc.d9'))
totalDEGs(c("treatment", 'n5','inc.d17'))
totalDEGs(c("treatment", 'n5','hatch'))
totalDEGs(c("treatment", 'n5','n9'))

totalDEGs(c("treatment", 'n9','bldg'))
totalDEGs(c("treatment", 'n9','lay'))
totalDEGs(c("treatment", 'n9','inc.d3'))
totalDEGs(c("treatment", 'n9','inc.d9'))
totalDEGs(c("treatment", 'n9','inc.d17'))
totalDEGs(c("treatment", 'n9','hatch'))
totalDEGs(c("treatment", 'n9','n5'))
```

>>>>

colData$group <- paste(colData$sex, colData$tempgroup, sep = "")
colData$group <- as.factor(colData$group)
str(colData$group)

colData$treatment <- factor(colData$treatment, levels = 
                              c("control", "bldg", "lay", "inc.d3", "inc.d9", 
                                "inc.d17", "hatch", "n5", "n9"))
```

@@

```{r resloop}
#create list of groups
a <- levels(colData$treatment)
a

# create list of groups, with control last
b <- a[2:9]
b[9] <- a[1]
b

for (i in a){
  for (j in b){
    print(paste(i,j))
    if (i != j) {
    numDEGs(i,j)
  }
  }
}
```
